---
title: "Is sample stranded?"
author: "Florent Chuffart, Céline Mandier"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
---


```{r, echo=FALSE, eval=TRUE}
knitr::opts_chunk$set(collapse=TRUE, comment = "#>", fig.width=9, fig.height=6, eval=TRUE, echo=FALSE, results="hide")
source("config")
```

# Data

Data matrix is compute from fastq files:

  * from study `r gse`
  * aligned on `r species` genome (UCSC) using STAR

Raw counts:

  * are computed using htseq-count
  * are normalized using DESeq2

We generate three tables corresponding to the count of reads for genes with htseq strand option set to:

  * `yes`
  * `no`
  * `reverse`

We plot raw counts obtained using `yes` option according to raw counts obtained using `reverse` option.

We plot characterization of reads `reverse` and reads `yes` with boxplot.


  
```{r}
print("# stranded or not?")
foo_no = read.table(paste0("~/projects/datashare/", gse, "/", gsm, "_notrim_star_Homo_sapiens_hg19_geneswchrm_strandedno_classiccounts.txt"     ))[,2]
foo_re = read.table(paste0("~/projects/datashare/", gse, "/", gsm, "_notrim_star_Homo_sapiens_hg19_geneswchrm_strandedreverse_classiccounts.txt"))[,2]
foo_ye = read.table(paste0("~/projects/datashare/", gse, "/", gsm, "_notrim_star_Homo_sapiens_hg19_geneswchrm_strandedyes_classiccounts.txt"    ))[,2]
layout(matrix(1:2, 1), respect=TRUE)
plot(log2(foo_re+1), log2(foo_ye+1), pch=".")
abline(0,1, col=2)
df = data.frame(cnt=c(log2(foo_re+1),log2(foo_ye+1)), str=c(rep("re", length(foo_re)), rep("ye", length(foo_ye))) )
boxplot(cnt~str, df)
```




# Session Information

```{r, results="verbatim"}
sessionInfo()
```





