---
title: "Is sample stranded?"
author: "Florent Chuffart, Céline Mandier"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
---


```{r, echo=FALSE, eval=TRUE}
knitr::opts_chunk$set(collapse=TRUE, comment = "#>", fig.width=9, fig.height=6, eval=TRUE, echo=FALSE, results="hide")
source("config")
```


# Data

Data matrix is compute from fastq files:

  * from study `r gse`
  * aligned on `r species    ` `r genome_version    ` `r annotation ` genome using STAR
  * counts are computed using `htseq-count`
  * normalization is done by DESeq2.

Raw counts are computed using htseq-count

We generate three tables corresponding to the count of reads for genes with htseq strand option set to:

  * `yes`
  * `no`
  * `reverse`

We plot raw counts obtained using `htseq-count stranded` option `yes` according to raw counts obtained using `htseq-count stranded` option `reverse`.

We plot characterization of reads `reverse` and reads `yes` with boxplot.


# Results
  
```{r}
print("# stranded or not?")
re_filenames = list.files(paste0("~/projects/datashare/", gse, "/"), paste0("*_notrim_star_", species, "_", annotation, "_", genome_version, "_", gtf_prefix, "_strandedreverse_classiccounts.txt"))
ye_filenames = list.files(paste0("~/projects/datashare/", gse, "/"), paste0("*_notrim_star_", species, "_", annotation, "_", genome_version, "_", gtf_prefix, "_strandedyes_classiccounts.txt"))
gsm = intersect(do.call(rbind, strsplit(re_filenames, "_notrim_star_"))[,1], do.call(rbind, strsplit(ye_filenames, "_notrim_star_"))[,1])
gsm
re_filenames = paste0("~/projects/datashare/", gse, "/", gsm, "_notrim_star_", species, "_", annotation, "_", genome_version, "_", gtf_prefix, "_strandedreverse_classiccounts.txt")
ye_filenames = paste0("~/projects/datashare/", gse, "/", gsm, "_notrim_star_", species, "_", annotation, "_", genome_version, "_", gtf_prefix, "_strandedyes_classiccounts.txt"    )
foo_re = read.table(re_filenames)[,2]
foo_ye = read.table(ye_filenames)[,2]
layout(matrix(1:2, 1), respect=TRUE)
plot(log2(foo_re+1), log2(foo_ye+1), pch=".")
abline(0,1, col=2)
df = data.frame(cnt=c(log2(foo_re+1),log2(foo_ye+1)), str=c(rep("re", length(foo_re)), rep("ye", length(foo_ye))) )
boxplot(cnt~str, df)
```

```{r}
diff = median(log2(foo_re+1)) - median(log2(foo_ye+1))

if (diff > 1.5) {
  strand = "reverse" 
} else if (diff < -2) {
  strand = "yes" 
} else {
  strand = "no"  
}

```

# conclusion

```{r echo=TRUE, results="verbatim"}
strand
```



# Session Information

```{r, results="verbatim"}
sessionInfo()
```





