---
title: "Material and Methods"
author: "Florent Chuffart"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
---


```{r, echo=FALSE, eval=TRUE}
knitr::opts_chunk$set(collapse=TRUE, comment = "#>", fig.width=9, fig.height=6, eval=TRUE, echo=FALSE, results="hide")
source("config")
```



# Material and Methods



## Sequencing

**FOLLOWING CONCERNS TGML PLATFORM** Total RNA was purified by trizol extraction followed by Qiagen RNeasy mini kit protocol. 
Removal of most rRNA was proceeded using NEBNext rRNA Depletion Kit Ribodepletion. 
Quality was verified by Agilent Bioanalyzer 2100. 
Libraries were prepared using NEBNext Ultra Directional RNA Library Prep kit for Illumina.
Base calling was performed using RTA version 2.*

Total RNA was purified by XXX.
Removal of most rRNA was proceeded using XXX.
Quality was verified by XXX. 
Libraries were prepared using XXX.
Base calling was performed XXX.

Stranded paired-end 2x75bp reads were produced by Illumina NextSeq500. 

**Alignment**

The fastq files were aligned on the `r annotation` `r version` genome using `STAR` (2.7.1a) [PMID:23104886] to produce bam files.

**Counts**

Bam files were counted using `HTSeq` framework (0.11.2) [PMID:25260700], with options:** -t exon -f bam -r pos --stranded=`r strand` -m intersection-strict --nonunique none


**Normalization and differential analysis**

Normalization and differential analysis were performed using the R software [R Core Team. R: A language and environment for statistical computing. Vienna, Austria : R Foundation for Statistical Computing, 2017], `DESeq2` (1.22.2) [PMID:20979621, PMID:25516281] and `SARTools` [PMID:27280887] packages.


**Quartile of expression**

We filtered non-zero counts protein-coding genes from NCBI Reference Sequence Database (RefSeq) and we organise genes by quartile of aboslute DESeq2 normalized expression in WT NFD 4 replicates. Quartile of expression genes were exported as bed files.

[abs_expr_q1_0.bed](./abs_expr_q1_0.bed) 
[abs_expr_q2_0.bed](./abs_expr_q2_0.bed)
[abs_expr_q3_0.bed](./abs_expr_q3_0.bed)
[abs_expr_q4_0.bed](./abs_expr_q4_0.bed)






# Session Information

```{r results="verbatim"}
sessionInfo()
date()
```



























